### 2019-01-15 Sections/economics_of_the_quantum_internet.tex
Added broken revote, added Cooperative enhancement (economics)

@@

>>>>

\sectionby{Scott Harrison \& Peter Rohde}

@@

\subsection{Cooperative enhancement}\index{Cooperative enhancement}

When implementing a quantum computation characterised by completely general computational scaling functions\index{Computational scaling functions}, $f^{X,Y}_\mathrm{sc}$ (which in general can be distinct for the two players $X$ and $Y$), elements in the payoff matrix associated with unification will be enhanced to \mbox{$(c_X,c_Y)$}, where,
\begin{align}
c_X &= \frac{n_X\cdot f^X_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y},\nonumber\\
c_Y &= \frac{n_Y\cdot f^Y_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y},
\end{align}
where the payoff matrix elements are assumed to be in units of classical-equivalent processing time, and resource sharing is based on the techniques for arbitrage-free time-share allocation presented in Sec.~\ref{sec:arb_free_time_share}.

Thus, it is evident that the enhancement in cooperative payoff matrix elements is highly dependent on:
\begin{itemize}
	\item The total number of qubits held by the two players.
	\item The asymmetry in the distribution of qubits between them.
	\item The respective algorithms to which the computational resources are being applied by each player.
\end{itemize}

The final point is particularly noteworthy, since it implies that optimal game-theoretic outcomes are not objective, but subjective, and highly dependent on how players are employing their computational resources, which may be highly asymmetric. If one player is employing an exponential scaling function, whereas the other is only employing a polynomial one, this could completely distort the dynamics of the game in favour of the player who would otherwise have been weaker under symmetric scaling functions. This in turn could completely alter the landscape of how users choose to optimally play.
